\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-29 document/ms.tex
Adding references for #23

Before the launch of the \kepler\ Mission, it was predicted that the nominal
mission would discover at least 10 exoplanets with only one or two observed
transits \citep{Yee:2008}, yet subsequent searches for these signals have
already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
However, the systematic study of the population of long-period exoplanets
found in the \kepler\ data to date has been hampered due to the
substantial technical challenge of implementing a search, as well as the
subtleties involved in intepreting the results. For example,
false alarms in the form of uncorrected systematics in the data and background
eclipsing binaries can make single-transit detections ambiguous.

@@

A study of the population of long-period transiting planets complements other
planet detection techniques, such as radial velocity \citep[for
example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
The marriage of the radial velocity and transit techniques is particularly
powerful as exoplanets with both mass and radius measurements can be used to
study planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
Unfortunately the existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods;  this makes discoveries with the transit method
at long orbital period compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

@@

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.
For both radial velocity and astrometry, there is information about the
orbiting planets in measurements made at all times~--~not just during transit.
This allows observations to be scheduled without a well constrained orbital
period.
Furthermore, follow-up of any of these candidates using radial velocity or
astrometry would provide a measurement of the density of a planet that would
be valuable for the study of planetary compositions.

>>>>

Before the launch of the \kepler\ Mission, it was predicted that the nominal
mission would discover at least 10 exoplanets with only one or two observed
transits \citep{Yee:2008}, yet subsequent searches for these signals have
already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
However, the systematic study of the population of long-period exoplanets
found in the \kepler\ data to date has been hampered due to the
substantial technical challenge of implementing a search, as well as the
subtleties involved in interpreting the results. For example,
false alarms in the form of uncorrected systematics in the data and background
eclipsing binaries can make single-transit detections ambiguous.

@@

A study of the population of long-period transiting planets complements other
planet detection and characterization techniques, such as radial velocity
\citep[for example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing
\citep[for example][]{Gould:2010, Cassan:2012, Clanton:2014,
Shvartzvald:2016}, direct imaging \citep[for example][]{Bowler:2016}, and
transmission spectroscopy \citep[for example][]{Dalba:2015}.
The marriage of the radial velocity and transit techniques is particularly
powerful as exoplanets with both mass and radius measurements can be used to
study planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
Unfortunately the existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods;  this makes discoveries with the transit method
at long orbital period compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

@@

\response{%
We note that in the above procedure we have not corrected our predictions
for the fact that our search has explicitly excluded KOIs
that host known \kepler\ EBs---if any of these excluded systems show fewer than
three eclipses and do not present both primary and secondary eclipses, then they
should also should perhaps count towards the number of EBs we should have
expected to find in this survey.  However, as the \kepler\ EB catalog does not provide information
on whether both primary and secondary eclipses are detected, we neglect this correction.
We note that this is a conservative decision, in the sense that accounting for the
effect of excluded EBs on our predictions would only further decrease the FPP of
the planetary signals, as they would be even less likely to be caused by EBs.
}

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up \citep{Beichman:2016, Dalba:2016}.
Instead, follow-up using radial velocity and astrometry are more promising.
For both radial velocity and astrometry, there is information about the
orbiting planets in measurements made at all times~--~not just during transit.
This allows observations to be scheduled without a well constrained orbital
period.
Furthermore, follow-up of any of these candidates using radial velocity or
astrometry would provide a measurement of the density of a planet that would
be valuable for the study of planetary compositions.
